cubble: An R Package for Structuring Spatio-temporal Data

### 2022-04-27 2-the-cubble-pkg.Rmd
Few comments on 2-the-cubble-pkg section

Each core function is introduced accompanied with a short example and the data `climate_flat` is used throughout this section. `climate_flat` contains five weather stations in Australia with spatial information of each station: station id, latitude, longitude, elevation, station name, World Meteorology Organisation ID and also daily temporal information of date, maximum and minimum temperature and precipitation for 2020. The first five rows of `climate_flat` are shown below:

>>>>

Each core \pkg{cubble} function is introduced and accompanied with a short example using the data `climate_flat`  throughout this section. `climate_flat` contains data on five weather stations in Australia including station id, latitude, longitude, elevation, station name, \textcolor{green}{World Meteorology Organisation ID and also information on the record's date (recorded daily) together with the maximum and minimum temperature and precipitation for 2020}. The first five rows of `climate_flat` are shown below:

### 2022-04-27 arxiv/cubble-arxiv.tex
Few comments on 2-the-cubble-pkg section

Each core function is introduced accompanied with a short example and the data \texttt{climate\_flat} is used throughout this section. \texttt{climate\_flat} contains five weather stations in Australia with spatial information of each station: station id, latitude, longitude, elevation, station name, World Meteorology Organisation ID and also daily temporal information of date, maximum and minimum temperature and precipitation for 2020. The first five rows of \texttt{climate\_flat} are shown below:

>>>>

Each core \pkg{cubble} function is introduced and accompanied with a short example using the data \texttt{climate\_flat} throughout this section. \texttt{climate\_flat} contains five weather stations in Australia with spatial information of each station: station id, latitude, longitude, elevation, station name, \textcolor{green}{World Meteorology Organisation ID and also information on the record's date (recorded daily) together with the maximum and minimum temperature and precipitation for 2020}. The first five rows of \texttt{climate\_flat} are shown below:
